Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-05-13 review/response/response.tex

  \item R2.2 \textit{First, while it is good that the authors included visually impaired individuals in the study, it is hard to know what to make of the differences in performance (and patterns of performance) between the two groups. Since the whole point of the study is to inform a system intended to be used by visually impaired individuals, how should we interpret this? The two groups are VERY different in performance, N, and (I assume, though details are not provided) demography. While having a group of young blind-folded participants is fine as a baseline for a project like this, the apparent variability and small N in the VI group is problematic. This isn’t really a fatal flaw, but it makes the study much less robust. At a minimum, we need to know more detail about the demographic details of the two groups. Currently, the paper lumps the age range and gender together for the two groups. Because the behavior of the two groups is so different, these really need to be separated.}
  \item[] We'd like to thank the reviewer for pointing this out. 
    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table meme. 
    We have also added comments in Section 5.3 to point out that these underlying demographic differences may be the cause of the divergences between the groups.  
    Furthermore, we added an additional Kolmogorov-Smirnov test in Section 5.3 to show the statistical similarity between the groups' results, which we hope alleviates concerns about robustness.

  \item R2.3 \textit{[...]Because the targets in this task are point targets, there is no W, so the authors used the spread of hits around the target to manufacture an effective width We. The problem with this is that the whole concept of We (from Crossman and then later Welford) *assumes that participants have some level of W that they are targeting*. Without this, there is no external feedback as to whether a user has actually hit the target or not—it’s just their own subjective sense. That is, ``accuracy'' in this case is essentially determined by the average subjective impression of individual participants (i.e., ``this seems right to me...click!'').  }
  \item[] Thank you for their insight.
    Firstly, we neglected to mention this in the text, but the targets were coded to have a 10cm radius, i.e. the 512Hz tone was emitted when the camera was within 10cm of the target centre (we have added this detail in Section 4.3).
    The frequency response plot in in Fig 2b has been adjusted to reflect this pseudo target width.
    This made the search process somewhat similar to the work by~\cite{kabbash1995prince}, who showed that searching for a point-target with an oversized cursor (analogous to the 10cm radius `searchlight' cursor in our case) is comparable to a normal Fitts-task with a target of known width being searched for with a point-cursor.
    Furthermore, we were not able to explicitly inform a user when they were within 10cm, because the goal of these experiments is mainly to determine the subjective impressions (as the reviewer put it) we can expect from a participant given some audio parameters.
    We have added text in Section 4.3 to point this out more explicitly and also point out that these experiments are at least conceptually similar to those that have been shown to be Fitts's Law-compliant by citing relevant literature.

@@

  \item R2.6 \textit{I suspect that the authors want to engage in this whole Fitts’s exercise in order to tie the work more closely to the wider HCI pointing literature. However, if the authors really wanted to use Fitts’s Law for this task, there is certainly precedent in the Marentakis \& Brewster, 2006 paper that they cite. Here, researchers used a second audio signal to indicate that a target was acquired.
    All the above notwithstanding, I’m not certain that this is *wrong* for the purposes they use here, it’s just very non-standard and violates much of the basic theory behind Fitts’s Law. So I don’t see this as a completely fatal flaw, but the authors would definitely need to modify the manuscript to address these issues if they want to engage with the Fitts’s Law discourse.}
  \item We appreciate this feedback.
    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target position estimation error.
    However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system.
    Regarding Fitts's Law not being used correctly in this work, we hope that the points in R2.3-2.4 sufficiently address the reviewer's concerns.

### 2020-05-13 paper.tex
Added extra references

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage[capitalise]{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{todonotes}

\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
\newcommand\hlbreakable[1]{\textcolor{red}{#1}}
\newtcolorbox{highlighted}{colback=yellow,coltext=black,breakable}

\citestyle{acmauthoryear}

@@

\begin{abstract}
  Sound perception is a fundamental skill for many people with severe sight impairments.
  The research presented in this paper is part of an ongoing project with the aim to create a mobile guidance aid to help people with vision impairments find objects within an unknown indoor environment.
  This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids. 
\end{abstract}

@@

\begin{highlighted}The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point. 
The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the advantages and limitations of its main user.
In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that will possibly benefit the user experience and boost long-term navigation performance.
\end{highlighted}

%This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the final part of their journey, addressing the so-called `last 10-yard problem'.
%Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
%In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
%However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.

@@

The system generates guidance instructions that can be interpreted in real-time with minimal additional cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

\begin{highlighted}
Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings. 
Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
The interface for this work is used to provide instructions to a stationary user to guide them to point a camera at a target location and we therefore are mainly concerned with micro-navigation tools. 
In this context, respondents with visual impairments typically prefer haptic and vocal feedback over an audio tone~\citep{arditi2013user,golledge2004stated}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.
\end{highlighted}
%Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

Work has been done in an attempt to spatialise these tones with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
However, the audio transmission device used has a significant effect on performance.
Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization}.
However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}, and found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions.
The measured performance is comparable to those of more expensive and over-ear headphones.

@@

\begin{highlighted}
Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities. 
Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance. 
\end{highlighted}

@@

\begin{highlighted}
Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences , ITD and ILD respectively) and monaural cues, where a cue is extracted directly from each ear's audio signal (e.g.\ the spectral profile, audio intensity).
The ITD and ILD extracted from binaural cues allow a user to localise a sound on the horizontal plane (e.g.\ a sound from the right will hit the right ear before left one), while monaural cues indicate a sound's distance (e.g. louder sounds appear closer than softer ones) and its position on the vertical plane (e.g.\ the spectral profile generated from the signal hitting the user's body).
Prior to transmitting an audio signal to the user, it can be adjusted by an HRTF to mimic a natural sound source and make a user believe it is located at some arbitrary 3D location. 
An HRTF is a mathematical function that simulates a human head and ear's response to an external sound and is derived by capturing key characteristics that affect the monaural and binaural responses at the user's ear, such as the hearing level and anatomy. 
An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.

The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}. 
However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
The pan angle can still be conveyed with a spatialised audio signal generated by an HRTF.
Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in~\citet{lock2019bone}.
\end{highlighted}

@@

\begin{highlighted}
To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
For example, a sound placed at a person's right will hit their right ear first with a slightly higher volume compared to the left ear.
Since the binaural cues are largely independent if the signal's spectral profile, it would be convenient to use a simple audio wave to transmit guidance instructions to the user.
Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}. %which uses the person and targets' positions as input, and outputs a transformed audio signal.}
\end{highlighted}

@@

\begin{highlighted}
To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
This high/low scheme was selected based on humans' natural association of high-pitched sounds with elevated objects and vice-versa for low-lying objects~\citep{pratt1930spatial,blauert1997spatial}.
The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}.

The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
This tone is heuristically set to \SI{512}{\hertz} following practical tests, which is comfortably audible for a large number of octaves changes.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.
\end{highlighted}

@@

We also compare the performance of the three pitch gradient settings in terms of the time it takes each participant to find a target.
However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
\begin{highlighted}
Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.
\end{highlighted}

\todo{mention limitations of Fitts, i.e. zero-width and not playing second tone to confirm target found}

%that we can use as a metric to compare the results between the three configurations.

@@

\noindent \hlbreakable{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}

@@

\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.}
Fitts's index of performance, $IP$, can then be calculated using

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
\hlbreakable{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception and none reported any significant prior experience with electronic navigation aids. }
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage[capitalise]{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
%\usepackage{soul}
%\usepackage{color}
\usepackage{todonotes}

%\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
\newcommand\hl[1]{\textcolor{red}{#1}}
%\newcommand\hl[1]{{\sethlcolor{yellow}\hl{#1}}}
\newtcolorbox{highlighted}{colback=yellow,coltext=black,breakable}
%\newcommand\hl[1]{%
  %\bgroup
  %\hskip0pt\color{yellow!80!black}%
  %#1%
  %\egroup
%}
%\sethlcolor{yellow}
\citestyle{acmauthoryear}

@@

\begin{abstract}
  Sound perception is a fundamental skill for many people with severe sight impairments.
  The research presented in this paper is part of an ongoing project with the aim to create a mobile guidance aid to help people with vision impairments find objects within an unknown indoor environment.
  This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law (a predictive model for human movement) can be used to generate a metric to improve and refine the quality of the audio interface in future mobile navigation aids. 
\end{abstract}

@@

\hl{The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance, are exploited to make this system possible.
In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
However, in the literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a target location. 
The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the user's strengths and limitations.
In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that could benefit the user experience and boost long-term navigation performance.}

@@

The system generates guidance instructions that can be interpreted in real-time with minimal additional cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from any arbitrary location.
In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a level of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
  The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}. 
Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
The interface for this work is used to provide instructions to a stationary user to guide them to point a camera at a target location and we therefore are mainly concerned with micro-navigation tools. 
In this context, respondents with visual impairments typically prefer haptic and vocal feedback over an audio tone~\citep{arditi2013user,golledge2004stated}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.}
%Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

Work has been done in an attempt to spatialise these tones with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized,presti2019watchout,crispien1994guib}.
However, the audio transmission device used has a significant effect on performance.
Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization,voong2019auditory,mascetti2016sonification}.
However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization,pec2008individual}.
Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}, and found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions.
The measured performance is comparable to those of more expensive and over-ear headphones.

@@

\hl{Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.}

\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities. 
Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}

@@

\hl{Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences , ITD and ILD respectively) and monaural cues, where a cue is extracted directly from each ear's audio signal (e.g.\ the spectral profile, audio intensity).
The ITD and ILD extracted from binaural cues allow a user to localise a sound on the horizontal plane (e.g.\ a sound from the right will hit the right ear before left one), while monaural cues indicate a sound's distance (e.g. louder sounds appear closer than softer ones) and its position on the vertical plane (e.g.\ the spectral profile generated from the signal hitting the user's body).
Prior to transmitting an audio signal to the user, it can be adjusted by an HRTF to mimic a natural sound source and make a user believe it is located at some arbitrary 3D location. 
An HRTF is a mathematical function that simulates a human head and ear's response to an external sound and is derived by capturing key characteristics that affect the monaural and binaural responses at the user's ear, such as the hearing level and anatomy. 
An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.}

\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}. 
However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
The pan angle can still be conveyed with a spatialised audio signal generated by an HRTF.
Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in~\citet{lock2019bone}.}

@@

\hl{To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
For example, a sound placed at a person's right will hit their right ear first with a slightly higher volume compared to the left ear.
Since the binaural cues are largely independent if the signal's spectral profile, it would be convenient to use a simple audio wave to transmit guidance instructions to the user.
Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.} %which uses the person and targets' positions as input, and outputs a transformed audio signal.}

@@

\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
This high/low scheme was selected based on humans' natural association of high-pitched sounds with elevated objects and vice-versa for low-lying objects~\citep{pratt1930spatial,blauert1997spatial}.
The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}. }

\hl{The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
This tone is heuristically set to \SI{512}{\hertz} following practical tests, which is comfortably audible for a large number of octaves changes.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.}

@@

We also compare the performance of the three pitch gradient settings in terms of the time it takes each participant to find a target.
However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
\hl{Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.}

@@

\noindent \hl{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}

@@

\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
\hl{The virtual targets have a programmed radius of approximately} \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
\hl{This is similar to the work by}~\citet{kabbash1995prince}\hl{, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
Previous authors have found this to capture the true performance metrics fairly well}~\citep{zhai2004speed}.
Fitts's index of performance, $IP$, can then be calculated using

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception and none reported any significant prior experience with electronic navigation aids. }
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
